\section{Model}
\label{sec:Model}

In this section, we present a simple theoretical model of driving behaviour, 
%
which guides our empirical specification. 
%
We use this to appeal to economic theory to determine whether to expect 
differences in age and gender as a result of a policy that increases the risk of driving, 
and if so, whether there would be a pattern in these differences. 
% 
We later use the conclusions reached from this analysis 
% as predictions of the results of the empirical model.
% ... i.e. we use it to guide our empirical specification
to provide testable predictions for the empirical analysis.  

Consider the utility maximization problem 
for the representative agent
%
% \begin{equation}
$$
	u_j (s) = g(s) - r_j (s)
$$
% \end{equation}
% 
where $g(s)$ is the utility of driving at speed $s$ 
and $r_j (s)$ is the disutility from the risk of driving at speed $s$, 
and $j$ indexes males and females $\{m,f\}$;
% 
therefore, we assume the representative male and the representative female 
have different risk preferences (and therefore utility functions). 
% 
Assume $g(s)$ is concave increasing $(g^{\prime} (s)>0, 
g^{\prime\prime} (s)<0)$ 
and $r_j (s)$ is convex increasing $(r_j^{\prime} (s)>0, r_j^{\prime\prime} (s)>0)$. 
Let $g(s)$ and $r_j (s)$ be continuous in the positive orthant. 
Impose the regularity conditions $g(s)\geq0 \forall s$ and $r_j (s)\geq0 \forall s$. 
Let there exist values of s such that $g(s)>r_j (s)>0$; 
this guarantees the existence of a non-trivial equilibrium. 
Taking the first order condition of the objective function, 
the ideal speed $s^*$ is chosen such that $g^{\prime} (s)=r_j^{\prime} (s)$, 
and this is a global maximum because 
$u_j^{\prime\prime} (s)=g^{\prime\prime} (s)-r_j^{\prime\prime} (s)<0$. 
Plotting each curve separately on a graph, 
the maximum point $s^*$ is the one such that 
the vertical distance between the concave and convex curves is maximized, 
and this occurs at the point where the slopes are equal. 
Let $r_m (s)<r_f (s)  \forall s$; 
that is, the perceived risk of driving at any given speed 
is higher for females than it is for males, 
% (Croson and Gneezy, 2009). 
following 
\citet{harris2006}
and consistent with
\citet{crosongneezy2009}.
Graphically, the risk function for the representative females will be more convex than it is for the representative male. 
Examining the first order conditions, 
we see that, on average, males will drive faster than females ($s_m^*>s_f^*$) 
since 
$u_m^{\prime} (s)
=g^{\prime} (s)-r_m^{\prime} (s)
>g^{\prime} (s)-r_f^{\prime} (s)
=u_f^{\prime} (s)$. \\


% Jeff says:
% I think we should set the proof in standard mathematical emphasis, i.e. the word "Proposition 1." in bold, the proposition itself in italics, and the word "Proof." in bold.
% In later drafts, I will use the proof environment.

\textbf{Proposition 1.} {\it Suppose the risk profile increases 
for both males and females such that driving at speed $s$ 
produces a risk of $r_j (s+\epsilon)$. 
Then, the decrease in driving speed for males will be greater 
than the decrease in driving speed for females.} \\

\textbf{Proof:} Let the new equilibrium point be labelled $s_j^{**}$. 
It is immediate that $s_j^*>s_j^{**}$ 
for both $j=\{m,f\}$ by the convexity of $r_j (s)$. 
By the concavity of $g(s)$ 
and because 
$r_m (s)<r_f (s)  \forall s, 
(s_m^*-s_m^{**} ) - (s_f^*-s_f^{**})>0$. \\




Informally, the female objective function for the representative female 
will reach its new equilibrium speed sooner 
because both $g(s)$ and $r_j (s)$ are steeper 
when moving from the old equilibrium to the new equilibrium.

This theoretical model predicts that people who are more risk averse 
towards a certain behaviour are less likely to be affected 
by additional disincentives for that behaviour. 
If the penalties for speeding increase, 
females are less likely to be affected because they are more risk averse. 
The model can analogously be applied to age: 
younger people tend to be more risk seeking 
% (e.g. Gong and Yang, 2011), 
% (e.g. \citet{gongyang2012}), 
\citep[e.g.][]{gongyang2012}, 
so we also predict that our empirical results will show that the effect of the law 
on risk taking behaviour in driving will decrease with age.



This leads us to the specify the following empirical model.
% 
We analyze the effect of the excessive speeding law on traffic tickets 
by means of an event study. 
The main regression specification is
%
% \begin{equation}
$$
y_{it} = \beta_0 + \beta_1 d_t
      + \bm{\beta}_2 d_t \bm{agecat}_{it} + \bm{\beta}_3 \mathbf{agecat}_{it}
      + \bm{\beta}_4 \bm{ptsgrp}_{it}
      + \bm{\beta}_5 \bm{calendar}_{it}
      + \varepsilon_{it}
$$
% \end{equation}
%
where $d_t$ is a dummy variable equal to 1 after the policy change and 0 before, 
$\mathbf{agecat}$ is a set of age category dummies, 
$\mathbf{ptsgrp}$ is a set of demerit point balance categories, 
$\mathbf{calendar}$ is a set of month and weekday indicator variables, 
and $\varepsilon_{it}$ is the usual error term.\footnote{% 
Note that the bolded items represent vectors rather than scalars.}
%  
The dependent variable $y_{it}$ is equal to 1 if individual $i$ received a ticket on day $t$ and 0 otherwise. 
The age category controls are 16 to 19, 20 to 24, 25 to 34, 35 to 44, 45 to 54, 55 to 64, and 65 and over. 
The demerit point balance is the sum of demerit points on a driver’s record over the last two years. 
This variable is divided in to categories of 1 to 3, 4 to 6, 7 to 9, and 10 and over.





% This could be the final paragraph of the Model section:
Our coefficients of interest are the scalar $\beta_1$ and the vector $\bm{\beta}_2$. 
We include the vector $\bm{\beta}_2$ in some specifications 
and run some regressions separating by gender because the theoretical model 
% of Section \ref{sec:Model} 
% Remove if Model section consolidated. 
above 
predicted the possibility of heterogeneous effects due to differential attitudes towards risk: 
females and those of higher ages are likely to be more risk averse. % \\





