\section{Introduction}
\label{sec:Introduction}

In 2018, 1,743 individuals died in Canada following a car accident (Transport Canada, 2020). Such accidents are the leading cause of death for individuals aged between 15 and 44 (Statistics Canada, 2020).  Many OECD countries have recently introduced harsher punishments to deter the types of behaviour that increase the likelihood of such tragedies. For example, penalties for speeding well above the speed limit now typically include some combination of substantially increased fines, immediate vehicle seizure, and license suspension. These laws are typically referred to as excessive speeding laws or stunt-driving laws.

Quebec followed this trend and introduced excessive speeding penalties in 2008. Its provisions are triggered when driving well above the speed limit. For example, driving at a speed of 100km/h in a 60km/h zone would be considered excessive speeding. These harsher punishments received widespread media coverage both before and after its implementation, and there was a sustained campaign by the provincial government to help ensure drivers were aware of the law. The Quebec government has since declared the legislation to be successful, with the number of excessive speeding tickets decreasing over time. Furthermore, the number of accidents with bodily harm decreased from 36,816 in 2006 to 32,371 in 2010, and the number of accidents with fatalities decreased from 666 to 441 over the same period (SAAQ, 2011). Even though these findings are encouraging, they don’t provide conclusive evidence that the harsher penalties truly caused changes in behaviour. The legislation has been unsuccessfully challenged in court.
Since Becker (1968), economists have theorized that harsher punishments alter the incentives of individuals and thus ultimately their behaviour. Helland and Tabarrok (2007) provide evidence for this mechanism studying the impact of California’s three-strike legislation on the recidivism rates of felons. However, the effectiveness of deterrence is unclear in the context of driving. Indeed, Bourgeon and Picard (2007) find that some drivers may be impossible to deter either because they do not care about the penalties or because they are not aware they are speeding.

A broad literature has investigated the role of deterrence on driving and alcohol consumption (e.g. Hansen, 2015), but less attention has been devoted to speeding. Some empirical research has determined the impact of very influential policies like the introduction of a demerit point system. For example, Benedettini and Nicita (2009) show a reduction in road fatalities through deterrence and incapacitation following the introduction of such a system. More generally, Castillo-Manzano and Castro-Nuño (2012) provide a meta-study demonstrating the broad positive impact of such a policy in a variety of countries. In Quebec, Dionne et al. (2011) focus on the threat of the loss of license on the behaviour of a driver close to the demerit point threshold of suspension. They find a reduction in the probability of violation for drivers with a large number of demerit points and conclude the system is successful in deterring the worst offenders.

In this paper, we investigate the effect of Quebec’s excessive speeding legislation on the frequency and types of violations incurred by Quebec drivers using an event-study design. Such violations are a proxy for driving behaviour, so this study will glean insight into the effect of increasing penalties on dangerous driving. It is important to note that we are looking at all violations which result in demerit points, and not just those that are affected by the change in the law. 

We begin with a simple theoretical model to examine the predictions of economic theory on the effect of the law on drivers. The model predicts the possibility of heterogeneous effects by age and gender. We then use driving records obtained from administrative data sets of the Government of Quebec comprising the universe of violations from 2006 to 2010 and records on drivers’ licenses over the same period. The use of large administrative datasets is necessary because only a small fraction of all drivers are impacted by the policy change; yet, these drivers are particularly important because they are generally responsible for accidents causing bodily harm and property damage. We examine the heterogeneous effects of the excessive speeding law on both the extensive (getting a ticket) and the intensive margin (getting a more severe ticket) across gender and age. 

We find that the daily probability of receiving a ticket (extensive margin) decreases after the implementation of the law. When we examine the results by age group, we find that the effects vary substantially, with young drivers between the ages of 16 and 24 being the most affected by the law, while there is little effect for drivers over the age of 45. Repeating the analysis by gender, we see that both males and females change their behaviour, but the magnitude of the effect on males is about eight times that of females. Examining the breakdown by age categories, we see that the effect gradually declines for males until age 55, while there appears to be no age effect for females. 
We then investigate the effect on the intensive margin. For males, the probability of getting tickets worth only one demerit point actually increases following the new policy, while tickets for all other point values decrease. This result suggests that male drivers are still exceeding the speed limit but are driving more slowly than before the introduction of the legislation. A similar pattern exists for female drivers for one and two point violations. We conclude that Quebec’s 2008 excessive speeding law has had substantial spillover effects on both the extensive and intensive margins of driving behaviour. In other words, not only has it reduced the number of drivers driving well above the speed limit, it has also led to a decrease in the propensity to commit other moving violations.

This paper contributes to the literature in several ways. It is the first examination using administrative data into the effect of an excessive speeding law on driving behaviour as proxied by violations by gender and age group. Such analysis is important, because most countries currently use demerit point systems. The question now is not whether these systems work but whether and how they can be adjusted to increase road safety. Moreover, this paper is to our knowledge the first one to empirically investigate the impact of such laws on both the intensive and extensive margins of speeding. Finally, by studying the impact of deterrence by gender and age, this paper fills a gap acknowledged by Freeman (1999) on the role of gender in studies surrounding criminality.

The rest of this article is organized as follows. Section 2 covers the details of Quebec’s excessive speeding law and the relevant institutional background. A simple theoretical model investigating the effects of the law is constructed in Section 3. The data and summary statistics are presented in Section 4. In Section 5, we conduct the empirical analysis. A series of robustness and placebo checks is conducted in Section 6. We conclude with a policy discussion in Section 7.
